---
title: "OSP-PBPK-Model-Library"
author: "Open Systems Pharmacology"
date: "`r Sys.Date()`"
output: github_document
---

Library of released PBPK substance models and evaluation reports

## How to create evaluation reports

- Create a new branch from the `create-reports` branch (for instance, `my-reports`)
  - Define the appropriate OSP environment and tools by updating `tools.csv`
  - Define the models and projects by updating `models.csv`
  - Go to the Github Action: [Automated Evaluation Reports and Projects](https://github.com/Open-Systems-Pharmacology/OSP-PBPK-Model-Library/actions/workflows/create-reports.yaml)
    - Click on the button __Run workflow__ 
      - Select your branch (for instance, `my-reports`)
      - Click on the green button __Run workflow__ 
  
## What to do when reports are created

When the evaluation reports are created, a pull request is triggered toward the `develop` branch.
The pull request will allow users to review the updates in the reports and adopt the new version.



<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
toolsData <- read.csv(
  "tools.csv",
  stringsAsFactors = FALSE,
  colClasses = "character"
)
modelsData <- read.csv(
  "models.csv",
  check.names = FALSE,
  stringsAsFactors = FALSE,
  colClasses = c("logical", rep("character", 5))
)
source("report-qualification-template.R")
```

```{r run reports, include=FALSE, warning=NA}
for (modelIndex in 1:nrow(modelsData)) {
  runEvaluationReport(modelIndex, modelsData, toolsData)
}
```

## Table of evaluated PBPK models

```{r, results='asis'}
knitr::kable(modelsData)
```

## Table of tools

```{r, results='asis'}
knitr::kable(toolsData)
```
